---
title: "Group 7 - Classification model for the default status"
author: "L. Becker, A. Chebatarova, A. Kandel, A.Kusche, R. Mizrak"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

# Introduction @ Anastasia

What is the project about? Who are we, what we are going to do?


# Init @ Anastasia
sajdkfjsdlkf jlaksdjf klasdjflk skladfs
af sdjflkjsdakl fksad f
sdafklsdjklf sad
f asd
f dsfldsjfk sajdf
```{r Initilize the environment, warning=TRUE}

  # Clear objects from the workspace
  rm(list=(ls()))
  
  # load library to deal with packages
  library(pacman)

  # install and loading required packages
  pacman::p_load(party, dummies, ranger, data.table, rmarkdown, tidyverse, caret, pls, corrplot, randomForest, foreach, plyr, tidyverse, magrittr, dplyr, tibble, doMC, pROC, class,MLmetrics, tree)
```
   

# Data Extraction @ Alex

In order to avoid to have to work with the whole original dataset from https://www.kaggle.com/wendykan/lending-club-loan-data
dataset_7.Rds has been created as follows.

``` 
loan_df <- read.csv(file = "loan.csv", header = TRUE)
loan_df <- cbind(id_2 = rownames(loan_df), loan_df)
rownames(loan_df) <- 1:nrow(loan_df)
loan_df$id_2 <- as.numeric(loan_df$id_2)
dataset_7 <- loan_df[which(loan_df$id_2%%8+1== 7),]
saveRDS(dataset_7, file = "dataset_7.Rds")

dataset_7 <- readRDS(file = "dataset_7.Rds")
```


  dataset <- readRDS(file = "dataset_7.Rds")
  
  
# General Exploration



# Data Preprocessing

sort dataset by colunm names
  dataset = dataset[ , order(names(dataset))]
  
  #removing policy_code because always equals 1
  dataset = subset(dataset, select = -c(policy_code) )
  
  
  # Removing columns that have > 0.05 NAs
  dataset <- dataset[, -which(colMeans(is.na(dataset)) > 0.05)]
  
  # Omiting columns that only have NAs, ie. id and member_id.
  dataset <- dataset[,colSums(is.na(dataset))<nrow(dataset)]
  
  # we remove desc as it is descrbing the purpose of the loan given it's unstructured data we can't do much about it.
  # Given we have a status column and date for all the factors that 
  # emp_title has too many levels to be used 
  # zip_code has too many levels and is a covariance of addr_state, thus we can remove it.
  
  # Too keep: earliest_cr_line could be an interesting variable to dummy code, we could transform it to only hold the year and make it a numerical value. same is true for sec_app_earliest_cr_line

  # last_pymnt_d and next_pymnt_d will be removed
  # addr_state is remove as it's not significant
  # grade is remove as it's a covariance of sub_grade
  dataset <- subset(dataset, select = -c(id_2, desc, emp_title, issue_d, title, zip_code, last_pymnt_d, next_pymnt_d, last_credit_pull_d, hardship_end_date, hardship_start_date, payment_plan_start_date, debt_settlement_flag_date, settlement_date, addr_state, grade) )

  # sub_grade has more than 32 levels which is a hard limit for random forest.
  # We'll dummy code it to circument this
  levels_sub_grade <- levels(dataset$sub_grade)
  dataset$sub_grade<- as.numeric(mapvalues(dataset$sub_grade, levels_sub_grade, seq(from = 1, to = 35, by = 1)))
  levels(dataset$sub_grade)
  
  # sorting emp_lenght, and dummy coding.
  levels_emp_length <- levels(dataset$emp_length)
  dataset$emp_length <- ordered(dataset$emp_length, levels = c("n/a", "< 1 year", "1 year", "2 years", "3 years","4 years", "5 years","6 years", "7 years", "8 years", "9 years", "10+ years"))
  levels(dataset$emp_length)
  dataset$emp_length <- as.numeric(mapvalues(dataset$emp_length, levels_emp_length, c(-1, seq(from = 0, to = 10, by = 1))))
  levels(dataset$emp_length)
  
  # grouping earliest_cr_line by year
  dataset$earliest_cr_line <- as.integer(substring(dataset$earliest_cr_line, 5))
  
  # grouping earliest_cr_line by year
  dataset$sec_app_earliest_cr_line <- as.integer(substring(as.character(dataset$sec_app_earliest_cr_line), 5))
  dataset$sec_app_earliest_cr_line[is.na(dataset$sec_app_earliest_cr_line)] <- -1
  typeof(dataset$sec_app_earliest_cr_line)
  levels(dataset$sec_app_earliest_cr_line)
  
  levels(dataset$total_rec_late_fee)
  
  na_count <-sapply(dataset, function(y) sum(length(which(is.na(y)))))
  
  # changing the dataset as a tbl object.
  dataset <- as.tbl(dataset)
  # change NAs to 0 in integer columns
  dataset <- mutate_if(dataset, is.integer, ~replace(., is.na(.), -1))
  # change NAs to 0 in doubles columns
  
  dataset <- mutate_if(dataset, is.numeric, ~replace(., is.na(.), -1))
  # change NAs to 0 in strings columns
  
  dataset <- mutate_if(dataset, is.character, ~replace(., is.na(.), "NA"))
  
  # change NAs to 0 in strings columns
  
  # dataset <- mutate_if(dataset, is.factor, ~replace(., is.na(.), "NA"))
  
  # change columns to character¨
  # dataset$hardship_type <- as.character(dataset$hardship_type)
  # dataset$hardship_reason <- as.character(dataset$hardship_reason)
  # dataset$hardship_status <- as.character(dataset$hardship_status)
  # dataset$hardship_loan_status <- as.character(dataset$hardship_loan_status)
  # dataset$settlement_status <- as.character(dataset$settlement_status)
  # dataset$verification_status_joint <- as.character(dataset$verification_status_joint)
  # 
  # change empty character columns to "NA"
  # 
  dataset <- mutate_if(dataset, is.character, ~replace(., is.na(.), "NA"))
  # 
  
  # calculating the number of unique levels per column
  sapply(dataset, function(col) length(unique(col)))
  
  na_count <-sapply(dataset, function(y) sum(length(which(is.na(y)))))
  
  return(dataset)



-----------
   
# Part 1 - Regression Analysis

## Preparatory tasks:
### Create a copy of your dataset, eliminating the entries that have an “na” in the interest rate variable int_rate. (Interest rate is used as output variable).
## Initialization

```{r initialization, message=FALSE, warning=FALSE, results="hide"}
source(file = "functions.R")
func_init_env()
```

```{r loading Rds file, results="hide"}
dataset <- func_data_load()
```

```{r preprocessing, echo=TRUE}
dataset <- func_data_prep(dataset)

sessionInfo()
```
### Apply the “validation set approach” to reserve a meaningful amount of data for the test phase.
```{r validation set approach, cache=TRUE}
# setting a seed for reproducability
set.seed(7)
# We randomly split our dataframe in a train and test set
trainRows = sample(1:nrow(dataset),0.5*nrow(dataset))
testRows = nrow(dataset) - trainRows
train = dataset[trainRows,]
test = dataset[testRows,]
# creating a small subset of data for quickly that models are runnining whithout any issues.
# This won't be used for the analysis
small_trainRows = sample(1:nrow(dataset),0.1*nrow(dataset))
small_testRows = sample(nrow(dataset) - small_trainRows,0.1*nrow(dataset))
small_train = dataset[small_trainRows,]
small_test = dataset[small_testRows,]
```
### Using one of the approaches for model selection discussed in class, reduce the number of predictors. For interpretability reasons, start with approaches that conserve the original predictor space. If any useful significant subset is possible, use a base transformation.

### Compute the correlation matrix for the selected set of predictors and the output variable, if useful, also using graphical representation.


## Data Exploration
```{r Data Exploration - interest rate vs loan amount}
# plotting the loan amount vs the interest rate
{ggplot(data = dataset, mapping = aes(loan_amnt, int_rate)) +
  geom_point()}
# from this visualisation we can't see any clear correlation.
```

```{r Data Exploration - interest rate vs term}
# plotting the loan amount vs the term
{ggplot(data = dataset, mapping = aes(term, int_rate)) +
  geom_boxplot()}
# Here we can see that the interest rate is generaly higher for 60 months loans and lower for 36 months loans.
```

```{r Data Exploration - interest rate vs grade}
# plotting the loan amount vs the grade
{ggplot(data = dataset, mapping = aes(factor(sub_grade), int_rate), group = 2) +
  geom_boxplot()}
# The sub_grade seems to have a strong influence on the interest rate
```

```{r Data Exploration - interest rate vs home ownership}
# plotting the loan amount vs home ownership
{ggplot(data = dataset, mapping = aes(factor(home_ownership), int_rate), group = 2) +
  geom_boxplot()}
# Here we can see that the interest rate is quite close to each other between home_ownership.
```

```{r Data Exploration - interest rate vs verification_status}
# plotting the loan amount vs verification_status
{ggplot(data = dataset, mapping = aes(factor(verification_status), int_rate), group = 2) +
  geom_boxplot()}
# The verification_status seems to also have an influence on the interest rate.

```

```{r Data Exploration - interest rate vs emp_title}
# plotting the loan amount vs verification_status
{ggplot(data = dataset, mapping = aes(factor(emp_title), int_rate), group = 2) +
  geom_boxplot()}
# The emp_title ????

```
```{r Data Exploration lm, cache=TRUE}
# lm on the whole dataset
if (exists(x = "lmp.fit") == FALSE){
readRDS("int_rate_lmp_fit")}
   else
lmp.fit=lm(int_rate~.,data = subset(dataset, select=c(-id_2)))

summary(lmp.fit)
plot(lmp.fit)
#removing features that do not have at least a 0.001 P value
dataset <- subset(dataset, select = -c(annual_inc, dti, earliest_cr_line,total_pymnt, total_rec_prncp, total_rec_int, total_rec_late_fee, recoveries, acc_open_past_24mths, avg_cur_bal, bc_open_to_buy, delinq_amnt, mo_sin_old_rev_tl_op, mo_sin_rcnt_rev_tl_op, mort_acc, num_il_tl, pct_tl_nvr_dlq, tax_liens, total_bal_ex_mort, total_bc_limit, total_il_high_credit_limit, num_actv_bc_tl, mo_sin_rcnt_tl))

# Donig a second round to see if further variables can be removed.
summary(lmp.fit)
lmp.fit=lm(int_rate~.,data = subset(dataset, select=c(-id_2)))

#removing features that do not have at least a 0.001 P value

dataset <- subset(dataset, select = -c(hardship_reason, inq_last_6mths, num_actv_rev_tl, percent_bc_gt_75, tot_hi_cred_lim))
                  
lmp.fit=lm(int_rate~.,data = subset(dataset, select=c(-id_2)))
summary(lmp.fit)

dataset <- subset(dataset, select = -c(bc_util))
                  
}}}

```

```{r}
lm.fit2=lm(int_rate~poly(sub_grade,2),data=dataset)
lm.fit4=lm(int_rate~poly(sub_grade,4),data=dataset)
lm.fit5=lm(int_rate~poly(sub_grade,5),data=dataset)
lm.fit6=lm(int_rate~poly(sub_grade,6),data=dataset)
lm.fit10=lm(int_rate~poly(sub_grade,10),data=dataset)
anova(lm.fit,lm.fit2,lm.fit4,lm.fit5,lm.fit6,lm.fit10, na.action = na.omit)

```
## Main task:
### Compare three different methods to perform regression, using the cross-validation method to compute the best parameters. Consider using some regularization for the parameters shrinkage. Test the train error rate, the CV error rate and the test error.

```{r stepwise model, results = FALSE, cache=TRUE, include=FALSE}

# should we use a gaussian model here?
null_model <- glm(int_rate ~ 1, data = subset(dataset[small_trainRows,], select=c(-id_2)), family = "gaussian")

# Specify the partial model using a subset of the potential predictors
partial_model <- glm(int_rate ~ ., data=subset(dataset[small_trainRows,], select=c(-id_2)), family = "gaussian")

#  -emp_title, -hardship_type, -issue_d, -desc, -title, -zip_code, -earliest_cr_line, -total_rec_late_fee, -last_pymnt_d, -next_pymnt_d, -last_credit_pull_d, -policy_code, -sec_app_earliest_cr_line, -deferral_term, -hardship_length, -debt_settlement_flag_date, -settlement_date

# This is taking too much time to process, stoped this at the 12th perdictor.
# Use a forward stepwise algorithm to build a parsimonious model
step_model <- step(null_model, scope = list(lower = null_model, upper = partial_model), direction = "forward", trace = 1)
# #  int_rate ~ sub_grade + all_util + loan_status + total_pymnt +
#     installment + initial_list_status + total_pymnt_inv + verification_status +
#     loan_amnt + term + out_prncp_inv + inq_fi + last_pymnt_amnt +
#     num_tl_op_past_12m + open_rv_12m + open_il_12m + sec_app_revol_util +
#     num_bc_tl + out_prncp + max_bal_bc + pub_rec + total_bc_limit +
#     open_acc + num_sats + purpose + total_rec_prncp

# Estimate the stepwise probability
step_prob <- predict(step_model, type = "response")

# getting the step response
step_response <- dataset[small_testRows,]$int_rate

# MAPE
MAPE(step_prob, step_response)
```

```{r stepwise model Both direction elimination , results = FALSE, cache=TRUE}
# should we use a gaussian model here?
null_model <- glm(int_rate ~ 1, data = subset(dataset[small_trainRows,], select=c(-id_2)), family = "gaussian")

# Specify the partial model using a subset of the potential predictors
partial_model <- glm(int_rate ~ ., data=subset(dataset[small_trainRows,], select=c(-id_2)), family = "gaussian")

step_model <- step(null_model, scope = list(lower = null_model, upper = partial_model), direction = "both", trace = 1)

saveRDS(step_model,"step_model_both")
# Estimate the stepwise probability for the test set.
step_prob <- predict(step_model, type = "response")
step_test_response <- dataset[small_testRows,]$int_rate

step_prob <- predict(step_model, type = "response")
step_train_response <- dataset[small_trainRows,]$int_rate
# MAPE for test set
MAPE(step_prob, step_test_response)
# MAPE for train set
MAPE(step_prob, step_train_response)

```

```{r, Ridge regression, results=FALSE}
library (car)
library (ridge)
library(lmridge)
vif(step_model)
model_testing <-lm(int_rate ~ sub_grade + out_prncp + open_acc + mo_sin_rcnt_rev_tl_op + total_rec_int +pct_tl_nvr_dlq + num_il_tl, data=small_train, na.action = na.omit)
predicted <- predict (model_testing, data=small_test)  # predict on test data
compare <- cbind (small_test$int_rate, predicted)  # combine actual and predicted
mean (apply(compare, 1, min)/apply(compare, 1, max))
linRidgeMod <- linearRidge(int_rate ~ sub_grade + out_prncp + open_acc + mo_sin_rcnt_rev_tl_op + total_rec_int +pct_tl_nvr_dlq + num_il_tl, data = small_train)
summary(linRidgeMod)
predicted <- predict(linRidgeMod, small_test)  # predict on test data
compare <- cbind (actual=small_test$int_rate, predicted)  # combine
mean (apply(compare, 1, min)/apply(compare, 1, max))
```

```{r Random Forest, results= False, cache=TRUE}
int_rate_RF <-  foreach(ntree=rep(125, 4), .combine=combine, .packages='randomForest')

int_rate_RF <- randomForest(int_rate ~., data=dataset, subset = small_trainRows, importance=TRUE, do.trace = TRUE)

int_rate_RF
summary(int_rate_RF)

class.error
plot(int_rate_RF)
fitted.int_rate=predict(int_rate_RF)

int_rate_RF_pred <- predict(int_rate_RF, newdata = dataset[small_testRows,])
view(int_rate_RF_pred)
table(int_rate_RF_pred, small_test$int_rate)
response_int_rate <- dataset[small_trainRows,]$int_rate
ROC <- roc(int_rate_RF_pred, response_int_rate)
plot(ROC, col = "red")
auc(ROC)
MAPE()
saveRDS(int_rate_RF, file = "int_rate_RF")
```
```{r Random Forest Ranger, cache= TRUE}
model2 <- train(int_rate ~ sub_grade, data = dataset[small_trainRows,], method = "ranger")
plot(model2)
```


```{r, Logistic regression, results=False}

fit_glm <- glm(int_rate ~. , data=subset(dataset, select=c(-id_2), family = binomial))
summary(fit_glm)
glm.probs <- predict(fit_glm, type = "response")
glm.probs[1:5]
#No idea how to interpet it
```
  
   @Axel
# Part 2 - Classification Analysis
## Preparatory tasks
### Our goal in the second part of the assignment is to predict if a new customer will be able to fully pay back their loans using a classification method. Thus, we concentrate on the "concluded lends" in the data set, i.e., on all lends whose loan_status is not Current. To this end, filter out all observations with loan_status == Current.
### For the remaining observations, check if the loan_status is “Fully Paid”. If not, change the value of loan_status to “DEFAULTED”
### Create a validation set. 


## Main tasks:

### Use Principal Component Analysis for base transformation and then compare it with the Partial Least Squares Regression result. Select the best base with cross validation, using the better of the two approaches.
### Perform the classification using KNN, Logistic Regression, Decision tree and Random forest.
### Compare the respective train and test error performances to select one of these approaches.
### Perform the prediction on the validation set and compute the confusion matrix.
### Conceptually compare your approach with a solution existing for this problem. (Default prediction is a very well-known problem in literature).

 @Alex
# Summary 







